Fast Radio Burst Cosmology

### 2014-06-19 writeup/dm_angular_ps.tex
small fixes.

@@

We assume parameters X, Y, Z etc.

\section{Short road to sensitivity}

The errorbar on the redshift averaged dispersion measure angular power spectrum
is
\begin{equation}
    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
\end{equation}
where the noise power spectrum is
\begin{equation}
    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
\end{equation}
Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
radio bursts.
%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.

$\sigma_D^2$ is the variance of the dispersion measures.  This would in
practice be measured directly from the observed set, but in terms of
theoretical parameters is
\begin{equation}
\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
\delta(z - z') p(z) w^{z z'}(1),
\end{equation}
where the first two terms are defined above in equations \ref{e:sig_nebar}
through
\ref{e:sig_src}. The third term is likely
neglidgable and could also be written as
\begin{equation}
    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
\end{equation}

>>>>

\begin{comment}

@@

% Note about cosmological parameters

\end{comment}

\section{Simplified sensitivity calculation}

In this section we present a simplified calculation for the sensitivity of the
above estimator which is valid for sample of observed
FRBs distributed roughly uniformly over some fraction of the sky.

The error bar on the redshift averaged dispersion measure angular power spectrum
is
\begin{equation}
    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
\end{equation}
where the noise power spectrum is
\begin{equation}
    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
\end{equation}
Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
radio bursts.
%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.

$\sigma_D^2$ is the variance of the dispersion measures.  This would in
practise be measured directly from the observed set, but in terms of
theoretical parameters is
\begin{equation}
\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
\delta(z - z') p(z) w^{z z'}(1),
\end{equation}
where the first two terms are defined above in equations \ref{e:sig_nebar}
through
\ref{e:sig_src}. The third term is likely
negligible and could also be written as
\begin{equation}
    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
\end{equation}
